RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-09-17 Response to reviewers2.txt

"We agree with the reviewer that a real validation of the approach is a necessary next step. However, we would like to point the reviewer to the case study in Section 3, in which 153 pages of transcripts of requirements discussions were used (see also the original materials at www.rationalgrl.com). We do agree that further validation of the tool and method is necessary, preferably in an industrial setting. However, such an industrial strength case study is a significant amount of work (see for example Estrada et al. (2006 "An empirical evaluation of the i* framework in a model-based software generation environment". They took 9 months to conduct the case study.), and would most likely yield enough new insights for a separate paper.

Since the main focus of our article is to explain the novel RationalGRL framework in detail, we feel that adding such an extensive study to the current article may be too much content. Still, we agree that having no validation at all is limiting, so we have performed a small-scale empirical study in order to provide an initial validation of our framework. This empirical study was performed amongst 16 participants, each with a computer science background."

===== ORIGINAL COMMENT #3
I think that the paper should compare the proposed argumentation structure at least with the beliefs in GRL. In general, how does this argumentation approach really differ from one based on beliefs and, in particular, belief revision? Assume that an argument is a belief of some stakeholder revised by another argument, which is a belief of some other stakeholder?

====== REPLY #3
In our first revision, we already added a brief comparison between arguments in RationalGRL and beliefs in GRL in the related work section (under "Beliefs in GRL"). In this revision, we have done two things. First, we have moved the discussion on beliefs in GRL to "related work" under "goal modeling" and further extended and sharpened our discussion and comparison with GRL beliefs. Our main argument, which is now fully in the article, is that in GRL, beliefs are more of an afterthought: they have no formal semantics and it is not possible to further reason with them (i.e. given indicated conflicts between beliefs compute ways in which beliefs can be revised).

### 2018-09-18 main.tex
Section 1-5
last changes

\title{RationalGRL: A Framework for Argumentation and Goal Modeling}
\author{Marc van Zee  \and Floris J. Bex\and Sepideh Ghanavati}
\institute{Marc van Zee \at Google BRAIN, Z\"urich, Switzerland \\\email{marcvanzee@gmail.com} 
\and Floris Bex \at Department of Information and Computing Sciences, Utrecht University, Utrecht, The Netherlands 
				\at Tilburg Institute for Law, Technology, and Society, Tilburg University, Tilburg, The Netherlands \\\email{f.j.bex@uu.nl}
\and Sepideh Ghanavati \at Department of Computer Science, Texas Tech University, Lubbock TX, USA \\\email{sepideh.ghanavati@ttu.edu} }

>>>>

\title{RationalGRL: A Framework for Argumentation and Goal Modeling}
\author{Marc van Zee  \and Floris J. Bex\and Sepideh Ghanavati}
\institute{Marc van Zee \at University of Luxembourg, Luxembourg (currently at Google Research, Z\"urich, Switzerland) \\\email{marcvanzee@gmail.com} 
\and Floris Bex \at Department of Information and Computing Sciences, Utrecht University, Utrecht, The Netherlands 
				\at Tilburg Institute for Law, Technology, and Society, Tilburg University, Tilburg, The Netherlands \\\email{f.j.bex@uu.nl}
\and Sepideh Ghanavati \at School of Computing and Information Science, University of Maine, Bangor, USA \\\email{sepideh.ghanavati@maine.edu} }
